A Switching Planner for Combined Task and Observation Planning

### 2011-02-08 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/switching.tex
spellers

Because online DT planning in large problems is impractical (we seek
response times in seconds), DT sessions plan in an abstract process
determined by the current trace and underlying belief-state. This
abstraction is constructed by first excluding all propositions (and
related actions) that are not true, or {\em assumed } true, of states
in the trace, then adding them back, using as a heuristic the entropy
of the trace assumptions conditional on a candidate
proposition. Propositions are added, one at a time, until the number
of states in the initial belief-state reaches a given
threshold.\footnote{Our experiments are performed using a number of
different threshold parameters.}  To the resulting abstract model we
also add {\em disconfirm} and {\em confirm} actions that the
DT session can schedule in order to judge an atomic assumption
in the trace. In the abstract model these actions yield a relatively
small reward if the corresponding judgement is true (or small penalty
otherwise). If a judgement action is scheduled for execution the
DT session is terminated, and control is returned to a
sequential session.

@@

The DT session plans in a {\em small} abstract processes defined
according to the assumptive actions in the proceeding trace, and the
$(\pp{:init})$ declaration that models the underlying
belief-state. Targeted sensing is encouraged by augmenting the reward
model to reflect a heuristic value of knowing the truth about
assumptions in the trace. In detail, all rewards from the original
POMDP are retained. Additionally, for each $\assumptiveS{i}$ action
scheduled by the current trace, we have a {\em dual}
$\assumptiveDT{i}$ so that forall states $\state$:

@@

\noindent where $\$(T_i)$ (resp. $\hat\$(T_i)$) is a 
relatively\footnote{Compared to rewards from the original process
model.} small positive (negative) numeric quantity which captures the
utility the agent receives for correctly (incorrectly) rejecting an
assumption. A dual action can only be executed once, and corresponds
otherwise to a self-transition -- I.e., except in the applicability of
the dual, the process remains in the state from which a dual is
executed.
%%
Furthermore, if \switchAction\ is the action that switched the system
to a DT session, then an assumption $\assumptiveS{i}$ is only {\em
active} if
\switchAction\ is not applicable in the sequential model unless
$\assumptiveS{i}$ is scheduled in the trace prefix
to \switchAction. We only include the duals of active assumptions in
DT sessions. Continuing our simplified example, if the trace is:

@@

The process posed to a DT session is abstract. The abstraction is
defined by first constructing an $(\pp{:init})$ declaration without
any-active assumptions from the trace -- E.g.,
(Fig.\ref{fig:abstraction-b}) gives an example, where diamonds are
probabilistic terms, and circles are atomic and/or conjunctive.
%%
For each excluded atom, we compute the {\em entropy} of the active
assumptions, {\em conditional} on that atom. Intuitively, lower
entropy indicates an atom gives better information about
assumptions. Facts are iteratively added to the belief-state in
increasing order according to that measure
(Fig.\ref{fig:abstraction-c}).

>>>>

Because online DT planning in large problems is impractical (we seek
response times in seconds), DT sessions plan in an abstract process
determined by the current trace and underlying belief-state. This
abstraction is constructed by first excluding all propositions (and
related actions) that are not true, or {\em assumed } true, of states
in the trace, then adding them back, using as an heuristic the entropy
of the trace assumptions conditional on a candidate
proposition. Propositions are added, one at a time, until the number
of states in the initial belief-state reaches a given
threshold.\footnote{Our experiments are performed using a number of
different threshold parameters.}  To the resulting abstract model we
also add {\em disconfirm} and {\em confirm} actions that the
DT session can schedule in order to judge an atomic assumption
in the trace. In the abstract model these actions yield a relatively
small reward if the corresponding judgement is true (or small penalty
otherwise). If a judgement action is scheduled for execution the
DT session is terminated, and control is returned to a
sequential session.

@@

The DT session plans in a {\em small} abstract processes defined
according to the assumptive actions in the proceeding trace, and the
$(\pp{:init})$ declaration that models the underlying
belief-state. Targeted sensing is encouraged by augmenting the reward
model to reflect a heuristic value of knowing the truth about
assumptions in the trace. In detail, all rewards from the original
POMDP are retained. Additionally, for each $\assumptiveS{i}$ action
scheduled by the current trace, we have a {\em dual}
$\assumptiveDT{i}$ so that for all states $\state$:

@@

\noindent where $\$(T_i)$ (resp. $\hat\$(T_i)$) is a 
relatively\footnote{Compared to rewards from the original process
model.} small positive (negative) numeric quantity which captures the
utility the agent receives for correctly (incorrectly) rejecting an
assumption. A dual action can only be executed once, and corresponds
otherwise to a self-transition -- i.e., except in the applicability of
the dual, the process remains in the state from which a dual is
executed.
%%
Furthermore, if \switchAction\ is the action that switched the system
to a DT session, then an assumption $\assumptiveS{i}$ is only {\em
active} if
\switchAction\ is not applicable in the sequential model unless
$\assumptiveS{i}$ is scheduled in the trace prefix
to \switchAction. We only include the duals of active assumptions in
DT sessions. Continuing our simplified example, if the trace is:

@@

The process posed to a DT session is abstract. The abstraction is
defined by first constructing an $(\pp{:init})$ declaration without
any-active assumptions from the trace -- e.g.,
(Fig.\ref{fig:abstraction-b}) gives an example, where diamonds are
probabilistic terms, and circles are atomic and/or conjunctive.
%%
For each excluded atom, we compute the {\em entropy} of the active
assumptions, {\em conditional} on that atom. Intuitively, lower
entropy indicates an atom gives better information about
assumptions. Facts are iteratively added to the belief-state in
increasing order according to that measure
(Fig.\ref{fig:abstraction-c}).
